Why Donors Donate?

### 2020-09-11 analysis/05_market_simulator.Rmd
added new posterior means
Changed theta to gamma

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(theta_mean = mean(Theta)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = theta_mean) %>% 
  select(-i)

>>>>

# Beta's of everything. The only model we care about right now
public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i)
